\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-23 bare_conf.tex
Bibliography fixes.

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\documentclass[10pt]{IEEEtran}
\usepackage{times}
\usepackage{color}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{etoolbox}
\usepackage[dvipsnames]{xcolor}
\usepackage{authblk}
\usepackage{blindtext}

@@

\bibitem{Bourne} R. R. A. Bourne et al. Vision Loss Expert Group. Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis. Lancet Glob Health. Vol. 5(9), pp. 888-897, 2017.

\bibitem{Caraiman} S. Caraiman et al. A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.

\bibitem{Csapo} A. Csap\'{o}, G. Wers\'{e}nyi, H. Nagy, and T. A. Stockman. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issue 4,  pp. 275-286, 2015.

\bibitem{Poggi} M. Poggi and S. Mattoccia. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.

\bibitem{Zientara} P. A. Zientara at al. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.

\bibitem{Owayjan} M. Owayjan, A. Hayek, H. Nassrallah, and M. Eldor. Smart Assistive Navigation System for Blind and Visually Impaired Individuals. 2015 International Conference on Advances in Biomedical Engineering (ICABME), pp. 162-165, 2015.

\bibitem{Dunai} L. D. Dunai, I. L. Lengua, I. Tortajada, and F. B. Simon. Obstacle detectors for visually impaired people. 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp. 809-816, 2014.

\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker. MUST: A Method for Participatory Design. Human Computer Interaction, vol. 13, no. 2, pp. 167-198, Jun. 1998.

\bibitem{Carroll} J. M. Carroll and M. B. Rosson. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.

\bibitem{Ren} Sh. Ren, K. He, R. Girshick, and J. Sun.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.

\bibitem{Liu} Ch. Liu, J. Mao, F. Sha, and A. Yuille. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.

\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.

\bibitem{Amos} B. Amos, B. Ludwiczuk, and M. Satyanarayanan. Openface: A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.

\bibitem{Laina} I. Laina, C. Rupprecht, V. Belagiannis, F. Tombari, and N. Navab. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.

@@

\bibitem{Valor} G. Varol, I. Laptev, and C. Schmid. Long-Term Temporal Convolutions for Action Recognition.  IEEE Transactions on Pattern Analysis and Machine Intelligence. Vol. 40, issue 6, pp. 1510-1517, 2016.

\bibitem{Tensorflow} M. Abadi et al. TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.

@@

\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com [retrieved: 1 2019].

\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech [retrieved: 1 2019].

\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html [retrieved: 1 2019].

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\documentclass[10pt]{IEEEtran}
\usepackage{times}
\usepackage{color}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{etoolbox}
\usepackage[dvipsnames]{xcolor}
\usepackage{authblk}
\usepackage{blindtext}
\usepackage{dirtytalk}

@@

\bibitem{Bourne} R. R. A. Bourne et al., \say{Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis,} Lancet Global Health, Vol. 5(9), pp. 888-897, 2017.

\bibitem{Caraiman} S. Caraiman et al., \say{A. Computer Vision for the Visually Impaired: the Sound of Vision System,} IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.

\bibitem{Csapo} A. Csap\'{o}, G. Wers\'{e}nyi, H. Nagy, and T. A. Stockman, \say{A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research,} Journal on Multimodal User Interfaces, Vol. 9, issue 4,  pp. 275-286, 2015.

\bibitem{Poggi} M. Poggi and S. Mattoccia, \say{A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning,} Proceedings of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.

\bibitem{Zientara} P. A. Zientara at al., \say{Third Eye: A shopping assistant for the visually impaired,} Computer, Vol. 50, Issue 2, pp. 16-24, 2017.

\bibitem{Owayjan} M. Owayjan, A. Hayek, H. Nassrallah, and M. Eldor, \say{Smart Assistive Navigation System for Blind and Visually Impaired Individuals,} 2015 International Conference on Advances in Biomedical Engineering (ICABME), pp. 162-165, 2015.

\bibitem{Dunai} L. D. Dunai, I. L. Lengua, I. Tortajada, and F. B. Simon,    \say{Obstacle detectors for visually impaired people,} 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp. 809-816, 2014.

\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker, \say{MUST: A Method for Participatory Design,} Human Computer Interaction, Vol. 13, Issue 2, pp. 167-198, Jun. 1998.

\bibitem{Carroll} J. M. Carroll and M. B. Rosson, \say{Participatory design in community informatics,} Design Studies, Vol. 28, Issue 3, pp. 243-261, May 2007.

\bibitem{Ren} Sh. Ren, K. He, R. Girshick, and J. Sun, \say{Faster R-CNN: Towards real-time object detection with region proposal networks,} Advances in Neural Information Processing Systems, pp. 91-99, 2015.

\bibitem{Liu} Ch. Liu, J. Mao, F. Sha, and A. Yuille, \say{Attention Correctness in Neural Image Captioning,} Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.

\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa, \say{Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces,} arXiv:1804.04118, [cs.LG], 2018.

\bibitem{Amos} B. Amos, B. Ludwiczuk, and M. Satyanarayanan, \say{Openface: A general-purpose face recognition library with mobile applications,} Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.

\bibitem{Laina} I. Laina, C. Rupprecht, V. Belagiannis, F. Tombari, and N. Navab, \say{Deeper depth prediction with fully convolutional residual networks,} Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.

@@

\bibitem{Valor} G. Varol, I. Laptev, and C. Schmid, \say{Long-Term Temporal Convolutions for Action Recognition,}  IEEE Transactions on Pattern Analysis and Machine Intelligence. Vol. 40, Issue 6, pp. 1510-1517, 2016.

\bibitem{Tensorflow} M. Abadi et al., \say{TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems,} arXiv:1603.04467, 2016.

@@

\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com [Retrieved: January, 2019].

\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech [Retrieved: January, 2019].

\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html [Retrieved: January, 2019].
